Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-12-04 2016-Weak-FH-Bisim/WeakBisim.tex
added WOT construction

\begin{example}
  Figure \ref{SimpleProtCounter:SpecOA-partial} show a partial view of the weak automaton of the simple protocol implementation.

\TODO{Explain the partial OA, and comment on building of WOT1}
\end{example}

\begin{figure}[t]
   \centerline{\includegraphics[width=12cm]{ATG/SPImplWeakOpen}}
  \caption{Weak Open Automaton, partial}
   \label{SimpleProtCounter:SpecOA-partial}
\end{figure}

>>>>

%% \begin{figure}[ht]
%%    \centerline{\includegraphics[width=12cm]{ATG/WOT1}}
%%   \caption{Construction of the Weak Open transition WOT1}
%%    \label{WOT1}
%% \end{figure}

\begin{figure}[ht]
   \centerline{\includegraphics[width=11cm]{ATG/WOT2}}
  \caption{Construction of WOT2}
   \label{WOT2}
\end{figure}

\begin{example}
  Figures \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA. We show on the top one possible sequence corresponding to a weak transition, on the bottom left the concerned subset of the original OA, and on the right the generated weak transition.
\end{example}

%  In the case of WOT1, we start with a tau loop, then change state with an action of hole $P$ to state 1, initializing the $ec$ counter. On state 1, we have two tau loops, on of them increasing the $ec$ counter. The resulting weak transition is represented here as a regular expression including assignemnts, rather than the substitutions of the formal definition. It can the be abbreviated as: $P\mapsto \texttt{p-send}\ \{(ec:=ec+1)^*$.

  WOT2 here is the transition delivering the result of the algorithm to hole $Q$. Remark that it includes a loop increasing the counter occurs before the action of $Q$, and this action is using the value of the counter. Let us go into the details, using rules WT1/2/3. For simplification we ignore the pure $\tau$-loops before and after the central \texttt{q-recv(ec)} action, they have no effect on the construction. First consider application of Rule WT3 on the first 3 transitions. Hole actions and predicates are empty, we just concentrate on the Post operations. Rule WT2 transforms each 3 OTs into WOTs. In the drawing we use \texttt{ec++} to abbreviate the Post: $\subst{ec\gets ec+1}$. Then WT3 produces the weak OT:
  $\openrule
         {\set{\tau}, True,
			\subst{\texttt{ec++}\shortotimes\texttt{ec++}\shortotimes\emptyset} }
         {s \OTWeakarrow {\tau\subst{\texttt{ec++}}} s'}$
         that you can rewrite as:      
  $\openrule
         {\emptyset, True,
			\subst{ec\gets ec+2} }
         {s \OTWeakarrow \tau s'}$

         Now you can iterate this construction an arbitrary number of times, getting for any natural number $n$ the weak transition:
  $\openrule
         {\emptyset, True,
			\subst{ec\gets ec+n} }
         {s \OTWeakarrow \tau s'}$

         For any of these, apply again WT3, using the central \texttt{q-recv(ec)} transition as $\alpha$, and you get:
      $\openrule
         {\gamma=\{\texttt{q-revc(ec)}\subst{ec\gets ec+n}\}, True,
			\subst{ec\gets ec+n} }
         {s \OTWeakarrow {\texttt{q-recv(ec)}\subst{ec\gets ec+n}} s'}$

  \begin{example}
    Figure \ref{SimpleProtCounter:WeakSpecOA} shows the weak automaton of the simple protocol specification.
    \TODO{comment...}
\end{example}

\begin{figure}[ht]
   \centerline{\includegraphics[width=10cm]{ATG/SPSpecWeakOpen}}
  \caption{Weak Open Automaton of the Specification}
   \label{SimpleProtCounter:WeakSpecOA}
\end{figure}

  \begin{example}
  Figure \ref{SimpleProtCounter:SpecOA-partial} shows a partial view of the weak automaton of the simple protocol implementation.

\TODO{Explain the partial OA}
\end{example}

\begin{figure}[t]
   \centerline{\includegraphics[width=12cm]{ATG/SPImplWeakOpen}}
  \caption{Weak Open Automaton of the implementation, partial}
   \label{SimpleProtCounter:SpecOA-partial}
\end{figure}
